### 2013-11-21 tests_Housing.Rmd
more data points for reg vs nonreg

```{r}
set.seed(101)

@@

save(report, file="Housing300_lambda0.8.vs.no.reg.Rda") # recover with load("Housing300.Rda")

>>>>

```{r}
set.seed(204)

@@

save(report, file="Housing300_lambda0.8.vs.no.reg_3.Rda") # recover with load("Housing300.Rda")

df <- data.frame(GA.Poly = report$ga.error,
                 GA.Poly.reg = report$ga.reg.error)

write.table(df, "Housing300_lambda0.8.vs.no.reg_3.txt")
